Graphs

### 2018-12-02 analysis/gaussmeanest.Rmd
Moved dsc results file.

Since the simulation experiments are very computationally intensive,
they are implemented separately (see the "dsc" directory in this git
repository), and here we only create plots to summarize the results of
these experiments.

@@

```{r load-results}
load("../output/gaus-dscr.RData")
```

>>>>

Since the simulation experiments are computationally intensive, they
are implemented separately (see the "dsc" directory in this git
repository), and here we only create plots to summarize the results of
these experiments.

@@

```{r load-results}
load("../output/dscr.RData")
```

### 2018-12-02 analysis/shiny.Rmd
Moved dsc results file.

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
load("../output/gaus-dscr.RData")
scenario_names = as.character(unique(res$scenario))
method_names = as.character(unique(res$method))

>>>>

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
load("../output/dscr.RData")
scenario_names = as.character(unique(res$scenario))
method_names = as.character(unique(res$method))
